Msc Thesis Figures

### 2021-03-06 docs/msc_thesis_figures.Rmd
reduce amount of files to be used

---
title: "Msc Thesis Figures"
author: "Valentin Lucet"
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = file.path(dirname(inputFile), 'index.html')) })
output:
  html_document:
    df_print: paged
    code_folding: hide
    self_contained: yes
    toc: yes
    toc_depth: 5
    toc_float:
      collapsed: yes
      smooth_scroll: no
  pdf_document:
    toc: yes
    toc_depth: '5'
params:
  REPRO_FIGS_ONLY: TRUE
---

@@

theme_set(theme_minimal())
theme_update(legend.position = c(0.85, 0.20),
             legend.box = "vertical",
             legend.background = element_blank(),
             legend.box.background = element_rect(colour = "black"),
             panel.border = element_rect(fill = NA),
             legend.title = element_text(size = 22),
             legend.text = element_text(size = 22),
             plot.title = element_text(size=22),
             plot.subtitle = element_text(size=22),
             axis.text.x = element_text(angle=65, vjust=0.6, size =22),
             axis.text.y = element_text(size =22),
             strip.text.x = element_text(size = 22),
             strip.text.y = element_text(22),
             axis.title=element_text(size=22))
```

@@

fig_1_static_chap_1 <- joined %>% 
  filter(climate != "none", chapter %in% c("none", "both", "chap_1")) %>% 
  group_by(scenarioId, species, iteration) %>% 
  group_modify(~mutate(.x , baseline = subset(.x, timestep == 2010)$sum_cur, 
                       the_diff = ((sum_cur-baseline)/baseline)*100 )) %>% 
  ggplot(aes(x=timestep, y=the_diff, col=climate)) +
  scale_color_manual(values = colors_sce$color, 
                     labels = c("Historic", "Baseline", "RCP 8.5")) +
  geom_smooth(aes(group = sce, linetype=code_run), alpha=0.5, method="loess") +
  #geom_point(aes(group = sce)) +
  scale_linetype_manual(values=c("solid", "twodash")) +
  facet_wrap(~species, scales = "fixed") +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  #geom_vline(xintercept = 2020, linetype = "dashed", color = "darkGreen", alpha = 0.5) +
  labs(y = "Current flow (% Change)",
       x = "Year",
       col = "Climate",
       linetype = "Run") +
  guides(col = guide_legend(ncol = 2, nrow=2), 
         linetype = guide_legend(nrow=1, override.aes = list(colour = 'black'))) +
  theme(legend.position = c(0.85, 0.15))+
  NULL
#fig_1_static_chap_1
ggsave(fig_1_static_chap_1, 
       filename = "../thesis/figures/connectivity_decrease_x5species_chap1.png", 
       width = the_width, height = the_height, dpi = the_dpi)
```

@@

```{r figure_1_model_2, message=FALSE, warning=FALSE, out.width="100%", fig.cap="Connectivity change for species through time, 2010-2100"}
fig_1_static_chap_2 <- joined %>% 
  filter(climate != "none", chapter %in% c("none", "both", "chap_2")) %>% 
  group_by(scenarioId, species, iteration) %>% 
  group_modify(~mutate(.x , baseline = subset(.x, timestep == 2010)$sum_cur, 
                       the_diff = ((sum_cur-baseline)/baseline)*100 )) %>% 
  ggplot(aes(x=timestep, y=the_diff, col=climate)) +
  scale_color_manual(values = colors_sce$color,
                     labels = c("Historic", "Baseline", "RCP 8.5")) +
  geom_smooth(aes(group = sce, linetype=code_run), alpha=0.5, method="loess") +
  scale_linetype_manual(values=c("solid", "dashed", "longdash", "dotted")) +
  facet_wrap(~species, scales = "fixed") +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  geom_vline(xintercept = 2020, linetype = "dashed", color = "darkGreen", alpha = 0.5) +
  labs(y = "Current flow (% Change)",
       x = "Year",
       col = "Climate",
       linetype = "Run") +
  guides(col = guide_legend(ncol = 2, nrow=2), 
         linetype = guide_legend(nrow = 2, ncol=2, 
                                 override.aes = list(colour = 'black'))) +
  theme(legend.position = c(0.85, 0.15))+
  NULL
#fig_1_static_chap_2
ggsave(fig_1_static_chap_2, 
       filename = "../thesis/figures/connectivity_decrease_x5species_chap2.png", 
       width = the_width, height = the_height, dpi = the_dpi)
```

@@

```{r roc_curves, eval=!(params$REPRO_FIGS_ONLY), message=FALSE, warning=FALSE, out.width="100%"}
# Roc curves data
urb <- readRDS("../data/temp/fit_rs_outcome_rf_urb_2.RDS")
agex <- readRDS("../data/temp/fit_rs_outcome_rf_agex_2.RDS")

@@

```{r 2010_compare_prep, eval=!(params$REPRO_FIGS_ONLY), message=FALSE, warning=FALSE, out.width="100%"}
list_of_files <-  list.files("../libraries/stsim/monteregie-conncons-scripted.ssim.output/Scenario-37/stsim_OutputSpatialState", full.names = T)
list_of_files <- list_of_files[grep(x=list_of_files, "ts2")]
stratum <- raster("../data/stsim/aggregated/primary_stratum_mont_or_not_or_PA.tif")
```

@@

```{r 2010_compare_urb, eval=!(params$REPRO_FIGS_ONLY), message=FALSE, warning=FALSE, out.width="100%"}
names <- paste0(c("historic_compare_agex", "historic_compare_urb"), ".png")

@@

```{r compare, eval=!(params$REPRO_FIGS_ONLY), message=FALSE, warning=FALSE, out.width="100%"}
source('../scripts/functions/draw_scenario.R')
for (scenario in c(39, 42, 45, 48, 51)){
  the_plot <- draw_scenario(scenario, mxp = mxp)
  the_name <- paste0("scenario_", as.character(scenario),"_compare.png")
  ggsave(plot = the_plot, 
         filename = paste0("../thesis/figures/",the_name), width = 30, height = 12, dpi = the_dpi)
}
```

>>>>

---
title: "Msc Thesis Figures"
author: "Valentin Lucet"
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = file.path(dirname(inputFile), 'index.html')) })
output:
  html_document:
    df_print: paged
    code_folding: hide
    self_contained: yes
    toc: yes
    toc_depth: 5
    toc_float:
      collapsed: yes
      smooth_scroll: no
  pdf_document:
    toc: yes
    toc_depth: '5'
---

@@

theme_set(theme_minimal())
theme_update(legend.position = c(0.85, 0.20),
             legend.box = "vertical",
             legend.background = element_blank(),
             legend.box.background = element_rect(colour = "black"),
             panel.border = element_rect(fill = NA),
             legend.title = element_text(size = 22),
             legend.text = element_text(size = 22),
             plot.title = element_text(size=22),
             plot.subtitle = element_text(size=22),
             axis.text.x = element_text(angle=65, vjust=0.6, size =22),
             axis.text.y = element_text(size =22),
             strip.text.x = element_text(size = 22),
             strip.text.y = element_text(22),
             axis.title=element_text(size=22))

# Set the REPROG_FIGS_ONLY
REPRO_FIGS_ONLY <- Sys.getenv("REPRO_FIGS_ONLY")
if(REPRO_FIGS_ONLY == ""){
  REPRO_FIGS_ONLY <- FALSE
} else {
  REPRO_FIGS_ONLY <- TRUE
}
```

@@

fig_1_static_chap_1 <- joined %>% 
  filter(climate != "none", chapter %in% c("none", "both", "chap_1"), species=="MAAM") %>% 
  group_by(scenarioId, species, iteration) %>% 
  group_modify(~mutate(.x , baseline = subset(.x, timestep == 2010)$sum_cur, 
                       the_diff = ((sum_cur-baseline)/baseline)*100 )) %>% 
  mutate(unique=paste0(sce, iteration)) %>% 
  ggplot(aes(x=timestep, y=the_diff, col=climate)) +
  scale_color_manual(values = colors_sce$color, 
                     labels = c("Historic", "Baseline", "RCP 8.5")) +
  #geom_smooth(aes(group = sce, linetype=code_run), alpha=0.5, method="loess") +
  geom_point(aes(group = sce), size=0.1) +
  geom_line(aes(group=unique, linetype=code_run))+
  scale_linetype_manual(values=c("solid", "twodash")) +
  facet_wrap(~species, scales = "fixed") +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  #geom_vline(xintercept = 2020, linetype = "dashed", color = "darkGreen", alpha = 0.5) +
  labs(y = "Current flow (% Change)",
       x = "Year",
       col = "Climate",
       linetype = "Run") +
  guides(col = guide_legend(ncol = 2, nrow=2), 
         linetype = guide_legend(nrow=1, override.aes = list(colour = 'black'))) +
  theme(legend.position = c(0, 0))+
  NULL
fig_1_static_chap_1
# ggsave(fig_1_static_chap_1, 
#        filename = "../thesis/figures/connectivity_decrease_x5species_chap1.png", 
#        width = the_width, height = the_height, dpi = the_dpi)
```

@@

```{r figure_1_model_2, message=FALSE, warning=FALSE, out.width="100%", fig.cap="Connectivity change for species through time, 2010-2100"}
fig_1_static_chap_2 <- joined %>% 
  filter(climate != "none", chapter %in% c("none", "both", "chap_2")) %>% 
  group_by(scenarioId, species, iteration) %>% 
  group_modify(~mutate(.x , baseline = subset(.x, timestep == 2010)$sum_cur, 
                       the_diff = ((sum_cur-baseline)/baseline)*100 )) %>% 
  mutate(unique=paste0(sce, iteration)) %>% 
  ggplot(aes(x=timestep, y=the_diff, col=climate)) +
  scale_color_manual(values = colors_sce$color,
                     labels = c("Historic", "Baseline", "RCP 8.5")) +
  #geom_smooth(aes(group = sce, linetype=code_run), alpha=0.5, method="loess") +
  geom_point(aes(group = sce), size=0.1) +
  geom_line(aes(group=unique, linetype=code_run))+
  scale_linetype_manual(values=c("solid", "dashed", "longdash", "dotted")) +
  facet_wrap(~species, scales = "fixed") +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  geom_vline(xintercept = 2020, linetype = "dashed", color = "darkGreen", alpha = 0.5) +
  labs(y = "Current flow (% Change)",
       x = "Year",
       col = "Climate",
       linetype = "Run") +
  guides(col = guide_legend(ncol = 2, nrow=2), 
         linetype = guide_legend(nrow = 2, ncol=2, 
                                 override.aes = list(colour = 'black'))) +
  theme(legend.position = c(0.85, 0.15))+
  NULL
fig_1_static_chap_2
#fig_1_static_chap_2
# ggsave(fig_1_static_chap_2, 
#        filename = "../thesis/figures/connectivity_decrease_x5species_chap2.png", 
#        width = the_width, height = the_height, dpi = the_dpi)
```

@@

```{r roc_curves, eval=!(REPRO_FIGS_ONLY), message=FALSE, warning=FALSE, out.width="100%"}
# Roc curves data
urb <- readRDS("../data/temp/fit_rs_outcome_rf_urb_2.RDS")
agex <- readRDS("../data/temp/fit_rs_outcome_rf_agex_2.RDS")

@@

```{r 2010_compare_prep, eval=!(REPRO_FIGS_ONLY), message=FALSE, warning=FALSE, out.width="100%"}
list_of_files <-  list.files("../libraries/stsim/monteregie-conncons-scripted.ssim.output/Scenario-37/stsim_OutputSpatialState", full.names = T)
list_of_files <- list_of_files[grep(x=list_of_files, "ts2")]
stratum <- raster("../data/stsim/aggregated/primary_stratum_mont_or_not_or_PA.tif")
```

@@

```{r 2010_compare_urb, eval=!(REPRO_FIGS_ONLY), message=FALSE, warning=FALSE, out.width="100%"}
names <- paste0(c("historic_compare_agex", "historic_compare_urb"), ".png")

@@

```{r compare, eval=!(REPRO_FIGS_ONLY), message=FALSE, warning=FALSE, out.width="100%"}
source('../scripts/functions/draw_scenario.R')
for (scenario in c(39, 42, 45, 48, 51)){
  the_plot <- draw_scenario(scenario, mxp = mxp)
  the_name <- paste0("scenario_", as.character(scenario),"_compare.png")
  ggsave(plot = the_plot, 
         filename = paste0("../thesis/figures/",the_name), width = 30, height = 12, dpi = the_dpi)
}
```
